---
title: "USC Single-Cell Omics Research and Education"
output:
  html_document: 
    toc: yes
    toc_depth: 3
    toc_float: true
layout: page
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load new packages, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

if (!require("here")) {install.packages("here"); require("here")}
```

# About

**University of Southern California Single-Cell Omics Research and Education (USC-SCORE)** is dedicated to driving excellence in the field of single-cell omics. We focus on applying and developing advanced methodologies to explore gene expression, epigenetics, proteomics, and spatial biology at the single-cell resolution. Our community is committed to training the next generation of scientists through workshops, seminars, and collaborative projects. We strive to uncover new insights into cellular diversity and its implications for personalized medicine and therapeutic innovation.

We meet on the **last Monday of the month from 4pm-5pm PST**.

Organizers:
  Jonathan Nelson (jnelson4@usc.edu)
  
# Email Signup

Click [**here**](http://eepurl.com/i5ptTQ) to join USC-SCORE and receive emails with the zoom link to attend.

# Upcoming Presentation Topics: 

| Date        | Topic          | Presenter  |
| :--------: |:-------------:| :-----:|
| January      | Updates to Seurat V5                                     | Jonathan Nelson |
| February     | Advances in scRNASeq Technologies                        | Jeremiah Reyes |
| March        | Best Practices for Reporting Data (GitHub/GEO)           | Jessica Bahena-Lopez |
| April        | Cell-Cell Interactions with CellChat                     | Kevin Burfeind |
| May          | Access to KPMP Datasets                                  | Xiao-Tong Su |
| June         | Spatial Transcriptomic Analysis                          | TBD |

# Previous Topics

### Installing R and R Studio with Seurat

#### Description

[**Link**](https://drive.google.com/drive/folders/1g5VKzv95DeIxfGaYfbKAKAotLiOld0DF?usp=sharing) to materials

### Downloading Files from GEO and other Seurat Functions

#### Description

[**Link**](https://drive.google.com/drive/folders/1_c0rTF99LIr7MpSBi-MqjCToNdjIWWEo?usp=sharing) to materials

### Advanced Data Visualization

#### Description

[**Link**](https://drive.google.com/drive/folders/1TaR9xpt0boFfyPON9Cv3O2RutXhrbdlg?usp=sharing) to materials

### Integrating Datasets with FindIntegrationAnchors()

#### Description

[**Link**](https://drive.google.com/drive/folders/1_bpbimP9VAMJ-h4RpAfALiTIBsuSQqvX?usp=sharing) to materials

### Working with Data Files and Dataframes

#### Description

[**Link**](https://drive.google.com/drive/folders/1r9qASJfO7qIdzqBdIv7BkChlFY1B33dS?usp=sharing) to materials

### Recreating Manuscript Figures

#### Description

[**Link**](https://drive.google.com/drive/folders/1yd1SMugaVh301uMcgTsoXGyz5MJorcH-?usp=sharing) to materials 

### Getting Fancy with ggplot2

#### Description

[**Link**](https://drive.google.com/drive/folders/16ES02R2Xbt1VIe4dm8KAPJTAzm9NiM2p?usp=sharing) to materials

### Pseudobulk and GSEA analysis

#### Description

[**Link**](https://drive.google.com/drive/folders/1grTN0UFqtAm3Mnc5kuWRtQKrcbL2fozY?usp=sharing) to materials

### Working with Complex Datasets

#### Description

[**Link**](https://drive.google.com/drive/folders/1ITiK7vPoaWjvW5F5Jhjm6xSs_-I1ur5F?usp=sharing) to materials

### 10X Genomics on Spatial Transcriptomics

#### Description

[**Link**](https://drive.google.com/drive/folders/1nq0009Jo7Q2_KsWaz6rH_2jwPG46jDIX?usp=sharing) to materials

### Biolegend on CITE-seq

#### Description

[**Link**](https://drive.google.com/drive/folders/17o2vR35N85_GcKTSgDSgMmo-HQBDMuvf?usp=sharing) to materials

### Cell Ranger and ShinyCell

#### Description

[**Link**](https://drive.google.com/drive/folders/1E3_Lw30ue6hWVMt_e0NUa6gtQPgGIJ2t?usp=sharing) to materials

### Isolating Nuclei

#### Description

[**Link**](https://drive.google.com/drive/folders/1hd5AeWM6-gF8LahkrluCKV9A-rt2iCSI?usp=sharing) to materials

### Using ChatGPT

#### Description

[**Link**](https://drive.google.com/drive/folders/1whKV0oDJ0m5A0dm1SgIak61pIKa5Ng1o?usp=sharing) to materials



