---
title: "USC Single-Cell Omics Research and Education"
output:
  html_document: 
    toc: yes
    toc_depth: 3
    toc_float: true
layout: page
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load new packages, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

if (!require("here")) {install.packages("here"); require("here")}
```

# About

**University of Southern California Single-Cell Omics Research and Education (USC-SCORE)** is dedicated to driving excellence in the field of single-cell omics. We focus on applying and developing advanced methodologies to explore gene expression, epigenetics, proteomics, and spatial biology at the single-cell resolution. Our community is committed to training the next generation of scientists through workshops, seminars, and collaborative projects. We strive to uncover new insights into cellular diversity and its implications for personalized medicine and therapeutic innovation.

Organizers:
  Jonathan Nelson (jnelson4@usc.edu)
  
# Email Signup

Click on this [**here**](http://eepurl.com/i5ptTQ) to join USC-SCORE.

# Upcoming Presentation Topics: 

| Date        | Topic          | Presenter  |
| :--------: |:-------------:| :-----:|
| January      | Updates to Seurat V5                                     | Jonathan Nelson |
| February     | Advances in scRNASeq Technologies                        | Jeremiah Reyes |
| March        | Best Practices for Reporting Data (GitHub/GEO)           | Jessica Bahena-Lopez |
| April        | Cell-Cell Interactions with CellChat                     | Kevin Burfeind |
| May          | Access to KPMP Datasets                                  | Xiao-Tong Su |
| June         | Spatial Transcriptomic Analysis                          | TBD |

# Previous Topics

### Installing R and R Studio with Seurat

#### Description

[**Link**](https://drive.google.com/drive/folders/1g5VKzv95DeIxfGaYfbKAKAotLiOld0DF?usp=drive_link) to materials

### Downloading Files from GEO and other Seurat Functions

Link to materials. 

### Advanced Data Visualization

Link to materials. 

### Integrating Datasets with FindIntegrationAnchors()

Link to materials. 

### Working with Data Files and Dataframes

Link to materials. 

### Recreating Manuscript Figures

Link to materials. 

### Getting Fancy with ggplot2

Link to materials. 

### Pseudobulk and GSEA analysis

Link to materials. 

### Working with Complex Datasets

Link to materials. 

### 10X Genomics on Spatial Transcriptomics

Link to materials. 

### Cell Ranger and ShinyCell

Link to materials. 

### Isolating Nuclei

Link to materials. 

### Using ChatGPT

Link to materials. 



